Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-16 WSSSPE3/report/wg_appendix_eng_design.tex
Update wg_appendix_eng_design.tex
Updates to main sections

\subsection{Summary of Discussion}
Software engineering principles form the basis of methods, techniques, methodologies and tools. This group discussed the principles of software engineering design for sustainable software and their application in various domains.

@@

\subsection{Plan for Future Organization}
The following plan for future organization was discussed:
\begin{itemize}
\item 
\item Organizing coordinating online calls via Google Hangout.
\end{itemize}

@@

\begin{itemize}
\item Ethic committee approval required for data collection.
\item 
\item 
\end{itemize}

>>>>

\subsection{Summary of Discussion}
Software engineering principles form the basis of methods, techniques, methodologies and tools. This group discussed the principles of software engineering design for sustainable software and their application in various domains including quantum chemistry and epidemiology.

@@

\subsection{Plan for Future Organization}
The following plan for future organization was discussed:
\begin{itemize}
\item Identify suitable undergraduate or post-graduate students.
\item Organizing coordinating online calls via Google Hangout.
\end{itemize}

@@

\begin{itemize}
\item Ethic committee approval required for data collection.
\end{itemize}
